### 2022-02-12 ms/PrestigeBias.tex
update

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \subcaption{Error scale is 0.01}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \subcaption{Error scale is 0.1}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
  \subcaption{Error scale is 1(=J)}  
  \end{subfigure}
  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
  \label{fig:num_sims}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
  \label{fig:hetro_mutation}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
  \label{fig:hetro_alpha}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$}
  \label{fig:var_beta}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{$1-\beta=s=0.005$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{$\alpha=0.1$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$}
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$}
  \label{fig:ch_env_k_l}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \subcaption{Error scale is 0.01}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \subcaption{Error scale is 0.1}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
  \subcaption{Error scale is 1(=J)}  
  \end{subfigure}
  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations. Demonstrates the similarities between the $\chi ^2$ metric of both models.}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$.
  Used to support the number of simulations needed for the DM approximation.}	
  \label{fig:num_sims}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
  Comparison of the DM approximation and the full model when mutation is included}	
  \label{fig:hetro_mutation}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.
  Comparison of the DM approximation and the full model when the indicator weight is homogeneous}	
  \label{fig:hetro_alpha}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$.
  Comparison of the DM approximation and the WF model for different values of the effective population size}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.
  Comparison of the DM approximation and the WF model for different values of the selection coefficient}
  \label{fig:var_beta}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{$1-\beta=s=0.005$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{$\alpha=0.1$}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$.
  Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients}
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.
  Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle}
  \label{fig:ch_env_k_l}
\end{figure}
